The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-28 paper/ms.tex
finished editing section on the triple peak

\subsection{Three-Peak Profiles}
\label{sec:3p}

@@

However, we find some cases where there is a possible signature of
three peaks. This is only present in some models ($\tau = 10^6,
V=100$\kms and $\tau = 10^7, V=300$\kms) and could be the result of
two competing effects: the rise in the line's center as the photons in
the photosphere escape in a single excursion and the broadening in the
two peaks as the photons closer from the center have to scatter to
escape.

%JEFR

As mentioned above Off-centered emission shows signs of three peak 
profiles, to analyse this in more detail we use the same method of the spheres
explained in \S \ref{sec:off-center}. We select spheres at $C=(\pm 0.25R, \pm0.5R, \pm0.75R)$ with a radii of
$0.25R$ for all the models, for those who present signs of three peak profiles such as 
$(V_{max}=50km$ $s^{-1}$ \& $\tau_{H}=10^{5}), (V_{max}=100km$ $s^{-1}$ \& $\tau_{H}=10^{6}), 
(V_{max}=200km$ $s^{-1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
with the aim of get stronger profiles.

Figure \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
a relation between optical depth, rotational velocity and $C$ must be accomplish.
In particular we found that for the outer spheres $C=\pm 0.75$ the three
peak arises for all of our models with $\tau_{\gamma}=10^{6}$ this is due to 
the fact that the wings of the line move away from the central part as $C$ increase. 
Another requirement is that a high optical depth must be balanced with a high velocity 
in order to make the wings and the central peak similar in 
height, for models in which the velocity is low spheres at $C = \pm 0.25$ produce 
noise three peak profiles due to the high value of $\tau_{H, r}$.

Figure \ref{fig:3p_res} show that even with a low resolution a three-peak profile 
would be observed, this is important for observational porpoises due to the finite 
spectral resolution.

>>>>

@@

However, we find some cases where there is a possible signature of
three peaks. This is only present in some models ($\tau = 10^6,
V=100$\kms and $\tau = 10^7, V=300$\kms) and could be the result of
two competing effects: the rise in the line's center as the photons in
the photosphere escape in a single excursion and the broadening in the
two peaks as the photons closer from the center have to scatter to
escape. We examine in greater detail these cases in the next
sub-section.

\subsection{Triple Peaked Profiles}
\label{sec:3p}

The off-centered cases with hints of triple peaked emision motivate us
to explore this in more detail. The first condition is to increase the
number of photons in the radiative transfer calculation. In the line
profiles presented in the previous subsection, only $\sim 10^4$ photons
have the geometric conditions to build the line profile. We run a few
models with $N_{\gamma} = 10^6$ in order to improve the statistics and
explore smaller radii for the off-centered spheres.

We re-simulate four models that presented some signs of triple peaked
profiles: $V_{\rm max}=50\kms$, $\tau_{\rm H}=10^{5}$; $V_{\rm
  max}=100\kms$, $\tau_{H}=10^{6}$; $V_{\rm max}=150\kms$, $\tau_{\rm
  H}=10^6$; and $V_{\rm max}=200\kms$, $\tau_{\rm H}=10^{7}$. We
select the photons that were emitted within spheres of radius $0.25R$
centered at $C=(0.25R, 0.5R, 0.75R)$, following the same
geometry presented in Figure \ref{fig:OCspheres}.

Figure \ref{fig:3p_profiles} summarizes the results for all these
models. In all cases the stronger triple peaked signatures is
presented by the emitting spheres close centered at $0.75R$ close to
the surface. Emitting spheres closer to the center do not show clear
signatures for a triple peaked emission.

Furthermore, taking into account all the models that do not event present hints for
a triple peaked emission it would seem that the rotational velocity
and optical depth must balance each other in order to show this feature
feature. Namely, if the rotational velocity is close to half the HFWM
of the line, the triple peaks are more likely to occurr. This is the
same threshold that in the case of centered emission marks the
difference between double and single peaked lines.

Are these features observable with current instrumental capabilities?
As an order of magnitude estimate we can consider that the width of
each one of the triple peaks is close to $1/3$ of the FWHM of the line
at a given $V_{\rm max}$. For the cases we have studied in this
subsection those values would be close to $50\kms$, $100\kms$ and
$200\kms$ for optical depths of $10^5$, $10^6$, and $10^7$
respectively. At a redshift of $z\sim 2-3$ each one of these widths
is multiplied by factors of $z+1\sim 3-4$. Considering a nominal value
for the resolution of $\Delta v=200\kms$ for a Near-IR spectrograph capable of observing
those galaxies \citep{Kulas12}, we find that only the case of triple
peaked emission for the most massive object $\tau_{\rm H}, 10^{7}$,
$V_{\rm max}=200\kms$ would have a chance to be spectrally resolved.

{\bf Figure \ref{fig:3p_res} show that even with a low resolution a three-peak profile 
would be observed, this is important for observational porpoises due to the finite 
spectral resolution. Seguro? Que es baja resolucion y que es alta
resolucion en este contexto?}
